---
title: "Comparison of transient infections across viruses and covariates"
output: pdf_document
toc: true
---

This file does the comparisons analysis of the CMV transient infections between other viruses, infants with primary infection or not, and with breastfeeding.

1) Compare viruses       
2) Compare by infection status    
3) Compare by breastfeeding 

```{r load data and packages, echo = F, warning = F, message = F}
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(scales)
library(knitr)
library(geepack)
library(readr)
library(xtable)
theme_set(theme_bw())

options(xtable.comment = FALSE)
options(xtable.include.rownames = FALSE)

load("data/all_blip_data.RData")

```

## Setup the data
```{r data setup}

blip_rates = arrange(all_blips, Virus, PatientID2) %>% group_by(Virus, PatientID2) %>%
  dplyr::summarize(blip_total = sum(count > 0),
                   total_swabs = n(),
                   infected = infantInfection[1],
                   total_time = as.numeric(difftime(max(times), min(times), units = "days")))

blip_rates$inf_label = factor(ifelse(blip_rates$infected == 1, "Yes", "No"),
                              levels = rev(c("Yes", "No")))
blip_rates$blip_prop = with(blip_rates, blip_total/total_swabs)

```

##1.) By virus

```{r viral comparisons, results="asis"}

blip_rates$Virus = factor(blip_rates$Virus, ordered = T)
blip_rates$Virus = with(blip_rates, reorder(Virus, -blip_prop))

blip_rates %>% group_by(Virus) %>% summarize(
    total = n(),
    mean = mean(round(blip_prop, 2)),
    median = median(round(blip_prop, 2)),
    IQR = paste(quantile(round(blip_prop, 2), c(0.25, 0.75)), collapse = ", "),
    range = paste(range(round(blip_prop, 2)), collapse = ", ")
) %>% xtable() %>% print()
```

```{r viral comparison plot, echo = F}

virus_prop_raw = ggplot(data = blip_rates,  aes(x = reorder(Virus, -blip_prop), y = blip_prop)) +
  geom_boxplot(fill = "grey") +
  scale_y_continuous("Proportion of swabs positive for viral DNA", limits = c(0, 0.7), breaks = 0.1 * 0:7) +
  scale_x_discrete("Virus", labels = c("CMV", "EBV", "HSV", "HHV-8", "HHV-6")) 

virus_prop = virus_prop_raw+
  theme(
    text = element_text(size = 15),
    axis.title.y = element_text(size = 12),
    axis.title.x = element_blank())

virus_prop

```


##2. By infant infection status

### all viruses
```{r infant infection comparisons, results="asis"}
blip_rates %>% group_by(Virus, inf_label) %>% summarize(
    total = n(),
    mean = mean(round(blip_prop, 2)),
    median = median(round(blip_prop, 2)),
    IQR = paste(quantile(round(blip_prop, 2), c(0.25, 0.75)), collapse = ", "),
    range = paste(range(round(blip_prop, 2)), collapse = ", ")
) %>% xtable() %>% print()
```

```{r infant infection comparisons plot, echo=FALSE}


all_prop_raw = ggplot(data = subset(blip_rates, Virus != 'HHV8'),  aes(x = Virus, y = blip_prop, fill = inf_label)) +
  geom_boxplot() +
  scale_y_continuous("Proportion of swabs positive for viral DNA", limits = c(0, 0.7), breaks = 0.1 * 0:7) +
  scale_fill_discrete("Primary infection\nobserved")+
   guides(fill=guide_legend(nrow=1, ncol = 2, title.position = "top", byrow = F)) 


all_prop = all_prop_raw+
  theme(
    legend.position = c(0.75, 0.65/0.7),
    text = element_text(size = 15),
    legend.text = element_text(size = 12), 
    axis.title.y = element_text(size = 12),
    axis.title.x = element_blank(),
    legend.background = element_blank())
all_prop

```

### CMV only
```{r infant infection comparisons cmv only, results="asis"}
subset(blip_rates, Virus == "CMV") %>% group_by(inf_label) %>% summarize(
    total = n(),
    mean = mean(round(blip_prop, 2)),
    median = median(round(blip_prop, 2)),
    IQR = paste(quantile(round(blip_prop, 2), c(0.25, 0.75)), collapse = ", "),
    range = paste(range(round(blip_prop, 2)), collapse = ", ")
) %>% xtable() %>% print()

```

```{r infant infection comparisons cmv only plot, echo=FALSE}

CMV_prop = ggplot(data = subset(blip_rates, Virus == "CMV"),  aes(x = inf_label, y = blip_prop)) +
  geom_boxplot(fill = alpha("grey", 0.75)) +
  scale_y_continuous("Proportion of swabs positive for CMV DNA", limits = c(0, 0.7), breaks = 0.1 * 0:7) +
  scale_x_discrete("CMV infection") +
  theme(
    text = element_text(size = 15),
    axis.title.y = element_text(size = 12))

CMV_prop

```

##3. Breastfeeding data

Note that consecutive positives are removed.

```{r bf analysis, warning = F, results="asis"}
ts_covariates = readr::read_csv("data/demographics_data.csv")

#extract negative swabs and then start of transient infections
cmv_blip_period =  subset(all_blips, Virus == "CMV") %>% 
    filter(!consecutive_swab | is.na(consecutive_swab)) %>% filter(pos) %>%
  bind_rows(subset(all_blips, Virus == "CMV" & !pos)) 

bf_pos_swabs = left_join(cmv_blip_period, ts_covariates, by =  c("PatientID2", "times")) %>%
  group_by(PatientID2) %>%
  mutate(
    breastfed_ever = max(breastfed),
    saliva_ever = max(saliva),
    chewfood_ever = max(chewfood)
  ) 

agg_function = function(var){
  subset(bf_pos_swabs, !is.na(get(var))) %>% group_by_(var) %>%
    dplyr::summarize(blip_total = sum(count > 0),
                     total_swabs = n(),
                     blip_prop = blip_total/total_swabs)
}

population_rates = bf_pos_swabs %>%
  group_by(PatientID2, breastfed_ever, saliva_ever, chewfood_ever) %>%
  summarize(
    blip_total = sum(count > 0),
    total_swabs = n(),
    blip_prop = blip_total/total_swabs
  ) %>%
  reshape2::melt(measure.vars = c("breastfed_ever", "saliva_ever", "chewfood_ever")) %>%
  group_by(variable) %>%
  mutate(
    total = n(),
    prop = mean(value)
  ) %>%
    group_by(variable, value, prop) %>%
  summarize(
    median_swabs = median(total_swabs),
    median_blip_prop = median(blip_prop),
    blip_prop_population = sum(blip_total)/sum(total_swabs)
  )

no_breastfeed_data = bf_pos_swabs %>%
  group_by(PatientID2) %>%
  mutate(
    no_bf_end_day = if(unique(breastfed_ever)) min(days[breastfed == 1]) else 
      max(days) + 1
  ) %>%
  subset(days < no_bf_end_day)

#any(no_breastfeed_data$breastfed)
#mean(no_breastfeed_data$count > 0)
#mean(subset(no_breastfeed_data, !breastfed_ever)$count > 0)
#no_breastfeed_data %>% group_by(PatientID2) %>% summarize(blip_prop = sum(count > 0)/n()) %>% summarize(mean_prop = mean(blip_prop))


covariate_rates = plyr::ldply(c("breastfed", "saliva", "chewfood"), function(x) {
  out = agg_function(x)
  z = which(colnames(out) == x)
  out$value = as.numeric(as.matrix((as.data.frame(out[, z]))))
  out$var = x
  out[, -z]
})


select(covariate_rates, var, value, everything()) %>% ungroup() %>% xtable(caption="Not by patient, by positive swab status") %>% print()

ungroup(population_rates) %>% xtable(caption="Positive swab proportion by patient. (population = pooled proportion).") %>% print()

```


```{r episode infection breastfeeding comparison, results="asis"}

bf_pos_swabs_all =  subset(all_blips, Virus == "CMV") %>%
  left_join(ts_covariates, by =  c("PatientID2", "times")) %>%
  group_by(PatientID2) %>%
  mutate(
    breastfed_ever = max(breastfed, na.rm = T), #there is a missing during a transient infection
    saliva_ever = max(saliva),
    chewfood_ever = max(chewfood)
  ) 

all_swab_rates = bf_pos_swabs_all %>%
  group_by(PatientID2, breastfed_ever, saliva_ever, chewfood_ever) %>%
  summarize(
    blip_total = sum(count > 0),
    total_swabs = n(),
    blip_prop = blip_total/total_swabs
  ) %>%
  reshape2::melt(measure.vars = c("breastfed_ever", "saliva_ever", "chewfood_ever")) %>%
  group_by(variable) %>%
  mutate(
    total = n(),
    prop = mean(value)
  ) %>%
    group_by(variable, value, prop) %>%
  summarize(
    median_swabs = median(total_swabs),
    median_blip_prop = median(blip_prop),
    blip_prop_population = sum(blip_total)/sum(total_swabs)
  )

ungroup(all_swab_rates) %>% xtable(caption="Positive swab proportion by all swabs. (population = pooled proportion).") %>% print()

```
